Implementing Real-Time Transport Services over an Ossified Network

### 2016-06-22 paper.tex
Expand discussion of codec/cc interactions, to address reviewer 2A comment

\newcommand{\fail}{\tikz\draw[red,fill=red] (0,0) circle (.5ex);}
\newcommand{\pass}{\tikz\draw[green,fill=green] (0,0) circle (.5ex);}
\newcommand{\okay}{\tikz\draw[orange,fill=orange] (0,0) circle (.5ex);}

@@

The TCP congestion control algorithm is executed by the end points, and
can be changed, provided the new version requires no new information to
be exchanged.
We note that, while standardised TCP congestion control has followed the
goal of maximising throughput at the expense of latency and variability,
this is not required by the protocol. TCP Vegas \cite{brakmo:1994:tcp-vegas}
is perhaps the best known approach that changes these constraints, with a
delay-based algorithm that reduces latency, although it is known to be less
aggressive than standard TCP, and is prone to starvation; FAST TCP 
\cite{jin:2004:fast-tcp} is a more modern delay-based algorithm that 
competes well with standard TCP in many environments, and is seeing 
commercial deployment. 
It would also be possible to
implement alternatives that seek stability, or compatibility with the
dictates of a video codec, rather than traditional ``TCP Friendly''
congestion control -- even if implemented within TCP.
The development of TCP congestion control shows that there might be
fairness issues as new algorithms are deployed, but the network does not
prevent the deployment of those algorithms.

@@

\begin{table}
  \centering
    \begin{tabular}{llcc}
    \toprule
    & ISP & Port 4001 & Port 80 \\ \midrule
    \textbf{Fixed-line} & Andrews \& Arnold & \pass & \pass \\
    & BT & \pass & \pass \\
    & Demon & \pass & \pass \\
    & EE & \pass & \pass \\
    & Eclipse & \pass & \pass \\
    & Sky & \pass & \pass \\
    & TalkTalk & \pass & \pass \\
    & Virgin Media & \pass & \pass \\ \midrule
    \textbf{Cellular} & EE & \okay & \okay \\
    & O2 & \okay & \okay \\
    & Three & \pass & \pass \\
    & Vodafone & \pass & \okay \\
    \bottomrule
    \end{tabular}
  \caption[]{Deployability of inconsistent retransmissions, where \pass \thinspace
  indicates successful delivery, \okay \thinspace indicates delivery of the original
  data, and \fail \thinspace indicates connection failure (none observed)}
  \todo{the labels need to be distinctive shapes, not just different colours}
  \label{tab:deployability}
\end{table}

>>>>

\newcommand{\fail}{\tikz\draw[red,fill=red] (0,0) rectangle (1.5ex,1.5ex);}
\newcommand{\pass}{\tikz\draw[green,fill=green] (0,0) circle (.75ex);}
\newcommand{\okay}{\tikz\draw[orange,fill=orange] (0,0) -- (0.75ex, 1.5ex) -- (1.5ex,0) -- cycle;}

@@

The TCP congestion control algorithm is executed by the end points, and
can be changed, provided the new version requires no new information to
be exchanged.
We note that, while standardised TCP congestion control has followed the
goal of maximising throughput at the expense of latency and variability,
this is not required by the protocol. TCP Vegas \cite{brakmo:1994:tcp-vegas}
is perhaps the best known approach that changes these constraints, with a
delay-based algorithm that reduces latency, although it is known to be less
aggressive than standard TCP, and is prone to starvation; FAST TCP 
\cite{jin:2004:fast-tcp} is a more modern delay-based algorithm that 
competes well with standard TCP in many environments, and is seeing 
commercial deployment.  The development of TCP congestion control shows
that there might be fairness issues as new algorithms are deployed, but the
network does not prevent the deployment of those algorithms.

It would also be possible to implement alternative congestion control
algorithms that seek stability, or compatibility with the dictates of a
video codec, rather than traditional ``TCP Friendly'' congestion control,
even if implemented within TCP.
To do this effectively might require changes to the interface between the
application and the TCP stack, even if the on-the-wire format remains the
same. For example, video applications generate data periodically, and it
might help the congestion control to know the period, so it can pace out
data; video traffic is less elastic than many TCP bulk flows, and it might
be benefical to inform the stack of an upper rate beyond which there is no
point increasing the congestion window, and a lower rate beyond which the 
flow cannot proceed; and informing the codec of the RTT and congestion
window might allow it to better schedule bursts of traffic to match the 
available capacity. In the interactive video conferencing community, 
\cite{draft-ietf-rmcat-cc-codec-interactions-02} addresses this issue for
congestion control over RTP on UDP/IP, but there is no analagous document
for TCP congestion control interactions as yet.

@@

\begin{table}
  \centering
    \begin{tabular}{llcc}
    \toprule
    & ISP & Port 4001 & Port 80 \\ \midrule
    \textbf{Fixed-line} & Andrews \& Arnold & \pass & \pass \\
    & BT & \pass & \pass \\
    & Demon & \pass & \pass \\
    & EE & \pass & \pass \\
    & Eclipse & \pass & \pass \\
    & Sky & \pass & \pass \\
    & TalkTalk & \pass & \pass \\
    & Virgin Media & \pass & \pass \\ \midrule
    \textbf{Cellular} & EE & \okay & \okay \\
    & O2 & \okay & \okay \\
    & Three & \pass & \pass \\
    & Vodafone & \pass & \okay \\
    \bottomrule
    \end{tabular}
  \caption[]{Deployability of inconsistent retransmissions, where \pass \thinspace
  indicates successful delivery, \okay \thinspace indicates delivery of the original
  data, and \fail \thinspace indicates connection failure (none observed)}
  \label{tab:deployability}
\end{table}
